Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
commit for ricardo

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations. Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications. Secondly, how to retain information from previous tasks whilst learning new tasks such as Continual Learning (CL, \cite{add})

>>>>

\section{Introduction}
\label{sec:intro}
%
Deep learning has become the cornerstone of contemporary artificial intelligence, proving remarkably effective in tackling supervised and unsupervised learning tasks in the {\em large data}, {\em offline}, and {\em gradient-based training} regime. Despite its success, gradient-based learning techniques exhibit limitations. Firstly how to incorporate uncertainty quantification over predictions which is needed in many applications. Secondly, if the data is from the same distribution

Secondly, how to retain information from previous tasks whilst learning new tasks where the tasks aresuch as Continual Learning (CL, \cite{add})

Thirdly and differently from the CL problem is that given some data from the same distribution
